\chapter*{Acknowledgements}
\textit{This Thesis represents the most important arrival point of a long journey that is my academic carrier at Politecnico di Milano. The number of people I've met during these years is enormous and each one of them taught me something that helped me in this journey or will help me in the future.}
\\
\textit{I want to thank both Professor Marcello Restelli and PhD. Pierre Liotet for they availability, support and patience during the development of the research and the writing of the thesis. Their advices and collaboration allowed me to be a proficient part of this research.}
\\
\textit{A lot of friends were made along the way and shared a piece of their journey with me. In particular, I would like to mention my Videogame Design and Programming project's group: Paolo, Umberto and Sasha. Working together on such a fun project is probably the best memory I have of this journey.}
\\
\textit{At last, I can't thank my family enough. Their continuous presence and support, both economically and personally, have been absolutely instrumental to pursue my studies freely without preoccupations other than successfully finish them. They endured my most tense periods like exam sessions or project deadlines, always putting their trust on my capabilities, even when I was unsure of them. In particular, I would like to dedicate this Thesis to my grandfather Domenico, whose interests in technology and innovation have been an inspiration for my academic and professional life.}